---
title: "warmup04-edmund-tian.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(ggplot2)
```

1.
```{r}
# assembling url so it fits on the screen
github <- 'https://raw.githubusercontent.com/ucb-stat133/stat133-hws/'
repo <- 'master/data/nba2018-players.csv'
datafile <- paste0(github, repo)

data_types <- cols(player = col_character(), team = col_character(), position = col_factor(), height = col_integer(), weight = col_integer(), age = col_integer(), experience = col_integer(), college = col_character(), salary = col_double(), games = col_integer(), minutes = col_integer(), points = col_integer(), points3 = col_integer(), points2 = col_integer(), points1 = col_integer())

dat <- read_csv(datafile, col_names = TRUE, col_types = data_types)
summary(dat)

typeof(dat)
```

2.
a. For printing, Tibbles have a refined print method that shows only the first 10 rows, and all the columns that fit on screen. This prevents the user from accidentlly overwhelming the console when printing large data frames. Tibble can extract by name or position.

b. Yes, you can use cols_only() to include only the columns you explicitly specify.

c. 
header = col_names
col.names = col_names
na.strings = na
colClasses = col_types


3.
```{r}
dat

grouped <- group_by(dat, team)
grouped

team_salaries <- summarize(grouped, total_salary = sum(salary) / 1000000, mean_salary = mean(salary) / 1000000, median_salary = median(salary) / 1000000)
team_salaries <- arrange(team_salaries, desc(total_salary))
team_salaries

as.data.frame(team_salaries)

ggplot(data = team_salaries, aes(x = reorder(team, total_salary), y = total_salary)) +
  geom_col() +
  coord_flip() +
  labs(tital = "NBA Team Ranked by Total Salary", x = "Team Name", y = "Total salary (in millions)") +
  geom_vline(xintercept = mean(team_salaries$total_salary), col = 'red')

```

4.
```{r}
team_points <- summarize(grouped, total_points = sum(points), mean_points = mean(points), median_points = median(points))
team_points <- arrange(team_points, desc(total_points))
team_points

as.data.frame(team_points)

ggplot(data = team_points, aes(x = reorder(team, total_points), y = total_points)) +
  geom_col() +
  coord_flip() +
  labs(tital = "NBA Team Ranked by Total Points", x = "Team Name", y = "Total points") +
  geom_vline(xintercept = mean(team_points$total_points), col = 'red')

```


5.
```{r}
points_salary <- inner_join(team_salaries, team_points, by = "team")
points_salary

summary(points_salary)

points_salary <- mutate(points_salary, cost_point = total_salary * 1000000 / total_points)
points_salary

summary(points_salary$cost_point)

ggplot(data = points_salary, aes(x = reorder(team, cost_point), y = cost_point)) +
  geom_col() +
  coord_flip() +
  labs(tital = "NBA Team Ranked by Point Cost", x = "Team Name", y = "Point Cost") +
  geom_vline(xintercept = mean(points_salary$cost_point), col = 'red')

ggplot(data = points_salary, aes(x = median_salary, y = median_points)) +
  geom_point() +
  geom_text(aes(label = team)) +
  geom_smooth(method = 'lm')
```
